ICM testing

### 2022-07-11 Scripts/ASR_stocks.Rmd
Update ASR_stocks.Rmd

---
title: "ICM testing"
output: html_document
---

@@

# OK, lets give this a spin...
funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
# Now run through a quick loop to load each one, just be sure that your working directory is read/write!
for(fun in funs) 
{
  download.file(fun,destfile = basename(fun))
  source(paste0(getwd(),"/",basename(fun)))
  file.remove(paste0(getwd(),"/",basename(fun)))
}

@@

@@

  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch,na.rm=T)) %>% pull(rem)
  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% pull(Year) %>% unique() %>% sort()
  N.end <- sum(data[data$Year==max(years),]$Num)
  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  vpa.abund <- data %>% group_by(Year) %>% summarize(vpa=sum(Num)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- as.numeric(min(data$age))
  #maxage
  maxage <- as.numeric(max(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
  #r.p.ssb
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  data$mx <- data$recs.per.age/data$ssn/2 # Moms only! Dividing by around 8 really nails it for NS cod for whatever reason :-)
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  # All the results in a plot
  print(ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i))
  # Same thing but functional boxplots
  print(ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  print(ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Estimated growth rate (r)") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i))
}
```

>>>>

---
title: "ICM testing"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

The stocks chosen for testing were those with the most complete data.

Some catch information was missing for certain years. These years are marked with "?" in the plots that follow. The median annual catch was assumed for missing years.

Catch data for _Sprattus sprattus_ (European sprat) was manually converted to be on the 1000s scale, in order to align with abundance data.

@@

# # OK, lets give this a spin...
# funs <- c("https://raw.githubusercontent.com/Dave-Keith/ICM/main/Scripts/functions/backwards_sim.r")
# # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
# for(fun in funs) 
# {
#   download.file(fun,destfile = basename(fun))
#   source(paste0(getwd(),"/",basename(fun)))
#   file.remove(paste0(getwd(),"/",basename(fun)))
# }

source("./functions/backwards_sim.R")

@@

  if(i=="ICES-WGBFAS_BS 22-32_Sprattus_sprattus") removals$Catch <- removals$Catch/1000

@@

  rem <- data %>% group_by(Year) %>% summarize(rem=sum(Catch)) %>% pull(rem)

  missing_rem<- NULL
  if(any(is.na(rem))) {
    missing_rem <- unique(data$Year)[which(is.na(rem))]
    rem[is.na(rem)] <- median(rem, na.rm=T)
  }

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% pull(Year) %>% unique() %>% sort()
  N.end <- sum(data[data$Year==max(years),]$Num)
  #N.end <- rowSums(abund[nrow(abund),-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  #vpa.abund <- rowSums(abund[,-which(names(abund) %in% c("Year", "Stock", "type"))], na.rm=T)
  vpa.abund <- data %>% group_by(Year) %>% summarize(vpa=sum(Num)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)
  #r.p.ssb
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  data$mx <- data$recs.per.age/data$ssn/2 # Moms only! Dividing by around 8 really nails it for NS cod for whatever reason :-)
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

  did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"

  # All the results in a plot
  print(ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
  # Same thing but functional boxplots
  print(ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?")))
  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  print(ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Estimated growth rate (r)") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i))
}
```
